Morse Theory

### 2020-11-29 paper.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin N2 
% % end N2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newpage
\section{Reeb graphs}
     \subsection{Introduction to Reeb graphs}
     \paragraph{}
      Suppose we have an equivalence relation, $\sim$, defined on a topological space $\X$. Let $\X_\sim$
      be the set of equivalence classes and let $\phi : \X \to \X_\sim$ map each point $x$ to its equivalence class.

     \paragraph{\textbf{Definition 1.2.1}}
      Let $f: \X \to \R$ be continuous and call a component of a level set a contour. Two
      points $x,y \in \X$ are equivalent if they belong to the same component of $f^{-1}(t)$
      with $t=f(x)=f(y)$. The Reeb graph of $f$, denoted as $R(f)=\X_\sim$, is the quotient space 
      defined by this equivalence relation.

      By construction, the Reeb graph has a point for each contour and the connection is 
      provided by the map $\phi:\X\to R(f)$. Letting $\pi:R(f)\to\R$ be defined such that $f(x)=\pi(\phi(x))$
      we can construct the level set by going backward, from the real line to the Reeb graph to the 
      topological space. Given $t\in\R$ we get $\pi^{-1}(t)$, a collection of points in $R(f)$,
      and $\phi^{-1}(\pi^{-1}(t))$, the corresponding collection of contours that make up the level set defined by $t$.

      \paragraph{Notes:}We have a continuous surjection $\phi:\X\to R(f)$ which maps components 
      to components. Furthermore, a loop in $\X$ that maps to a loop in $R(f)$ is not contractible
      and two loops in $\X$ that map to different loops in $R(f)$ are not homologous. It follows
      that the number of components is preserved and the number of loops cannot increase:
      $$
      \beta_0(R(f))=\beta_0(\X)
      $$
      $$
      \beta_1(R(f))\le\beta_1(\X)
      $$

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin N2 
% % end N2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
